Introduction

### 2024-11-27 intro.qmd
Use APA citation style
Add a background on research compendia to introduction

---
title: "Introduction"
lang: en
bibliography: literature.bib
---

Together, we will create a research compendium whilst taking the following ten things into account [@Arguillas2022]:

@@

>>>>

---
title: "Introduction"
lang: en
---

In the following, we will provide a brief introduction to the concept of _research compendia_.

## The importance of sharing

Suppose you are reading an article about a new imaging method to turn seismological data into subsurface images. The article describes the ideas that went into developing this method and presents a few examples to illustrate its superiority over previous approaches. You got interested and would like to apply this method to your own data. However, with only the article available, it could take months to come up with a working solution, if possible at all. This situation has been put aptly by @Buckheit1995, distilling an idea by Jon Claerbout:

> "An article about computational science in a scientific publication is not the scholarship itself, it is merely advertising of the scholarship. The actual scholarship is the complete software development environment and the complete set of instructions which generated the figures."

Even for articles that are use computers to apply existing methods (rather than reporting on a new method), sharing the source code and being transparent about the computational environment is imperative to making research reproducible [@Ince2012]. By reproducibility, we mean "obtaining consistent results using the same input data; computational steps, methods, and code; and conditions of analysis" [@NASEM2019, p. 46].

## Linking results and computations

This tutorial not only covers sharing the source code, but also connecting it to the results through the creation of dynamic documents. Rather than manually copying numerical results, figures, or tables, they are inserted automatically upon rendering of the article. Dynamic documents bundled together with any necessary data and auxiliary software are called a [research compendium](https://research-compendium.science/) [@Gentleman2007].

The practice to interleave narrative text with code has its roots in the paradigm of literate programming, where documentation and source code are treated as equals and are arranged in a way to maximize understanding [@Knuth1984]. Alternating text and code can be also found in notebook interfaces for exploratory programming, such as provided by Wolfram Mathematica or Jupyter Notebooks [@Kluyver2016], with the added capability of executing the code and embedding its output. With _Sweave_ [@Leisch2002], ideas from both worlds -- literate programming and embedding program output -- were combined into one tool for rendering dynamic documents using the R programming language. It is the predecessor of the R package `knitr` [@Xie2015] which is being used under the hood in this tutorial.^[Specifically, Quarto employs `knitr` to execute chunks of R code.]

Linking results with their computations has benefits for authors and readers. For the author, articles always contain the most recent version of figures, as they are updated automatically when the computation changes. For the readers, it enables understanding exactly how a particular result was obtained if they get access to the underlying research compendium.

## Best practices

When creating the research compendium, there are a few things to consider [by @Arguillas2022, licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/)]:

@@

Although this tutorial guides you through the creation of a research compendium, you are invited to revisit these questions after completion and check whether and how each point was addressed (or not). Further, you can consult them as a checklist for future projects.
